Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-10-14 paper.tex
Dubious humor?

With climate change threatening the Planet, storing only 16 bits in a
32 bits word would be borderline unethical. We can further increase
register usage and instantly double throughput by processing two
blocks at the same time. To this end, we introduce a new Naperian
functor, \coqe!Double.T!, indexed by the two elements set \coqe!Fst!
and \coqe!Snd!. This leads to
%
\coqfrom{Skinny/Bitslice}{state}
%
which denote our intent to manipulate objects of type \coqe!reg32! as
if they were stored in a single machine word. In the present work,
this observation will remain at the state of wishful thinking. One can
think of the code in this section (as well as the fixsliced code, in
the next section) as playing, themselves, the role of specifications
to lower-level refinements. Our previous work on Usuba suggests that
we will be able to deliver on this promise in the future. Further,
remark that the \coqe!state! now corresponds to two intermingled
blocks but as we shall process them in lock-step throughout the
cipher, this does not make much difference.

>>>>

% With climate change threatening the Planet, storing only 16 bits in
% a 32 bits word would be borderline unethical.

Storing only 16 bits in a 32 bits word (on \textsc{Arm} Cortex M)
remains sub-optimal. We can further increase register usage and
instantly double throughput by processing two blocks at the same
time. To this end, we introduce a new Naperian functor,
\coqe!Double.T!, indexed by the two elements set \coqe!Fst!  and
\coqe!Snd!. This leads to
%
\coqfrom{Skinny/Bitslice}{state}
%
which denote our intent to manipulate objects of type \coqe!reg32! as
if they were stored in a single machine word. In the present work,
this observation will remain at the state of wishful thinking. One can
think of the code in this section (as well as the fixsliced code, in
the next section) as playing, themselves, the role of specifications
to lower-level refinements. Our previous work on Usuba suggests that
we will be able to deliver on this promise in the future. Further,
remark that the \coqe!state! now corresponds to two intermingled
blocks but as we shall process them in lock-step throughout the
cipher, this does not make much difference.
